Preregistration analysis, Cost 2 study

### 2019-05-14 Cost2/Cost2_prereg.Rmd
added a section on mean forced travels as a function of time, and cleaned inattentive data

This plot shows the AIC for every model. The figure below shows AIC and BIC for all the models. As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`).

@@

@@

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost$propBlocks <- dataAll %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
                         ggplot(aes(Block, propAccept, fill = Cost)) +
                           geom_point(size = 2, pch = 21, color = "black") +
                           geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line(aes(color = Cost)) +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = cols) +
                           scale_fill_manual(values = cols) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.25),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 16))

@@

``` {r Testing plots, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 4}
# a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
# for each cost separately.
# think of doing it for the block order and then prop accepted across costs
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(BlockOrder = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
#     geom_point(size = 3) + 
#     #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
#     geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
#     #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(Cost), ncol = 2) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))

# now for each first block experienced, how do costs compare per reward x handling
dataAll %>%
  group_by(SubjID) %>%
  mutate(FirstBlock = case_when(
    Handling[1] == 2 ~ "Two",
    Handling[1] == 10 ~ "Ten",
    Handling[1] == 14 ~ "Fourteen",
  )) %>%
  group_by(Cost, Handling, Reward, FirstBlock) %>%
  summarise(pAccept = mean(Choice),
            SE = sd(Choice) / sqrt(length(Choice))) %>%
  ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
    geom_point(size = 3) + 
    geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
    geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
    labs(x = "Reward.Handling", y = "Proportion Accepted") +
    scale_color_manual(values = cols) +
    facet_wrap(vars(FirstBlock), ncol = 3) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

# # now also separated by half
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(FirstBlock = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(Cost, Handling, Reward, FirstBlock, Half) %>%
#   summarise(pAccept = mean(Choice),
#             SE = sd(Choice) / sqrt(length(Choice))) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
#     geom_point(size = 3) + 
#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(Half, FirstBlock), ncol = 3) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))
```

>>>>

@@

This plot shows the AIC for every model. The figure below shows AIC and BIC for all the models. As predicted, the model with all main effects reduced the deviance the most ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`). The reduction in deviance from an intercept-only model was drastic enough that we did not compute an LRT.

@@

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost$propBlocks <- dataAll %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = cols) +
                           scale_fill_manual(values = cols) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.25),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 16))

@@

``` {r Testing plots, echo = FALSE, fig.align = "center", fig.width = 6, fig.height = 4}
# a facet grid of p(acceptances) as a function of reward x handling, distinguishing between first handling time experienced,
# for each cost separately.
# think of doing it for the block order and then prop accepted across costs
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(BlockOrder = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(SubjID, Cost, Handling, Reward, BlockOrder) %>%
#   summarise(pAccept = mean(Choice)) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, linetype = BlockOrder, color = BlockOrder)) + 
#     geom_point(size = 3) + 
#     #geom_errorbar(aes(ymin = meanComplete - SE, ymax = meanComplete + SE), width = 0.2, size = 1) +
#     geom_line(aes(group = interaction(Handling, SubjID)), size = 1) +
#     #geom_point(aes(y = round(optimal)), shape = 21, fill = "grey75", color = "grey30", size = 3, show.legend = F) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(Cost), ncol = 2) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))

# # now for each first block experienced, how do costs compare per reward x handling
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(FirstBlock = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(Cost, Handling, Reward, FirstBlock) %>%
#   summarise(pAccept = mean(Choice),
#             SE = sd(Choice) / sqrt(length(Choice))) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
#     geom_point(size = 3) + 
#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(FirstBlock), ncol = 3) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))

# # now also separated by half
# dataAll %>%
#   group_by(SubjID) %>%
#   mutate(FirstBlock = case_when(
#     Handling[1] == 2 ~ "Two",
#     Handling[1] == 10 ~ "Ten",
#     Handling[1] == 14 ~ "Fourteen",
#   )) %>%
#   group_by(Cost, Handling, Reward, FirstBlock, Half) %>%
#   summarise(pAccept = mean(Choice),
#             SE = sd(Choice) / sqrt(length(Choice))) %>%
#   ggplot(aes(interaction(Reward, Handling), pAccept, color = Cost)) + 
#     geom_point(size = 3) + 
#     geom_errorbar(aes(ymin = pAccept - SE, ymax = pAccept + SE), width = 0.4, size = 1) +
#     geom_line(aes(group = interaction(Handling, Cost)), size = 1) +
#     labs(x = "Reward.Handling", y = "Proportion Accepted") +
#     scale_color_manual(values = cols) +
#     facet_wrap(vars(Half, FirstBlock), ncol = 3) +
#     theme(legend.key = element_blank(),
#           panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(), 
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"),
#           text = element_text(size = 16))

# forced travels as a function of time
# number of forced travels as a function of time for cognitive and grip trials
forcedTravels <- dataAll %>%
  filter(rawChoice == 2) %>%
  group_by(SubjID, Cost, Block) %>%
  count() %>%
  group_by(Cost, Block) %>%
  summarise(mTravels = mean(n),
            SE = sd(n) / length(Block))

tempphys <- tibble(Cost = as.factor(rep("Physical", 6)),
                   Block = as.numeric(seq(6)),
                   mTravels = rep(0, 6),
                   SE = rep(0, 6))

forcedTravels <- full_join(forcedTravels, tempphys)

  ggplot(data = forcedTravels, aes(Block, mTravels, color = Cost )) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    geom_errorbar(aes(ymin = mTravels - SE, ymax = mTravels + SE), width = 0.4) +
    scale_x_continuous(breaks = seq(6)) +
    labs(y = "Mean number of forced travels") +
    ylim(0, 4) +
    theme(legend.key = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))
```
